Issues with Dynamical Measurements Across the Disk

### 2019-04-06 paper/ms.tex
final revisions to the introduction

Lacking an empirical, nonlocal definition of the global Galactic midplane or a measurement of the expected midplane variation in the Milky Way itself,  in Section~\ref{sec:local_fire} we attempt to quantify the azimuthal dependence of the
local midplane, and hence the expected size of the dynamical solar neighborhood, using cosmological-hydrodynamical zoom-in simulations of Milky Way-mass galaxies from the Feedback in Realistic Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}} \citep{2016ApJ...827L..23W,2017arXiv170206148H}.  In Section \ref{sssec:neighborhood} we use these estimates to consider, as an example, the feasibility of one science goal that relies on the invariance of actions --- the reconstruction of open clusters across large distances using ``dynamical tagging;'' that is, the association of stars to a birth cluster based on their similar actions. In light of our findings, we considered the orbits of the
nine open clusters within $250\,\pc$ as reported by the {\em Gaia}
collaboration \citep{2018AA...616A..10G}. In Table~\ref{tab:real_clusters}, we
report the distance to each cluster, the three actions, and the maximum
vertical extent of their orbits ($z_{\text{max}}$). 
%The actions are computed using the technique described in Section~\ref{ssec:action_comp}. 
 In Section~\ref{sssec:reconstruction} we estimate and discuss the size of the dynamical solar neighborhood for each cluster based on its mass, to show that action-space tagging is likely still a viable method if background is unimportant. In Section~\ref{sec:discussion} we discuss further implications for action-space analyses beyond the dynamical solar neighborhood. We summarize and conclude in Section~\ref{sec:conclusion}.

>>>>

Lacking an empirical, nonlocal definition of the global Galactic midplane or a measurement of the expected midplane variation in the Milky Way itself,  in Section~\ref{sec:local_fire} we attempt to quantify the azimuthal dependence of the
local midplane, and hence the expected size of the dynamical solar neighborhood, using cosmological-hydrodynamical zoom-in simulations of Milky Way-mass galaxies from the Feedback in Realistic Environments (FIRE)
collaboration\footnote{\url{https://fire.northwestern.edu}} \citep{2016ApJ...827L..23W,2017arXiv170206148H}.

In Section~\ref{sec:discussion} we discuss the implications of midplane variations, and the resulting systematic uncertainty in the vertical action, for action-space analyses beyond the dynamical solar neighborhood. As an illustration, in Section \ref{sssec:neighborhood} we use these estimates to consider the feasibility of one science goal that relies on the invariance of actions --- the reconstruction of open clusters across large distances using ``dynamical tagging;'' that is, the association of stars to a birth cluster based on their similar actions. In light of our findings, we considered the orbits of the
nine open clusters within $250\,\pc$ as reported by the {\em Gaia}
collaboration \citep{2018AA...616A..10G}. In Table~\ref{tab:real_clusters}, we
report the distance to each cluster, the three actions, and the maximum
vertical extent of their orbits ($z_{\text{max}}$). 
%The actions are computed using the technique described in Section~\ref{ssec:action_comp}. 
 In Section~\ref{sssec:reconstruction} we estimate and discuss the size of the dynamical solar neighborhood for each cluster based on its mass, to show that action-space tagging is likely still a viable method if background is unimportant.  We summarize and conclude in Section~\ref{sec:conclusion}.
